\documentclass[main]{subfiles}


\title[Advanced Hyperparameter Optimization]{Advanced Hyperparameter Optimization}
\subtitle{Warmstarting}
\author[Katharina Eggensperger]{Katharina Eggensperger}
\date{}

%\institute{}
%\date{}

\begin{document}
	
	\maketitle
	

%----------------------------------------------------------------------
%----------------------------------------------------------------------
\begin{frame}[c]{Should we always start from scratch?}

$\leadsto$ Does provide the most unbiased result, but may not be efficient enough in practice.

<here is a nice picture of a cookie and a speech bubble with the text "How would you create a new cookie recipe?">

\end{frame}
%-----------------------------------------------------------------------
%----------------------------------------------------------------------
\begin{frame}[c]{Let's consider two settings}


\textbf{Case 1:} We have prior observations on the \textit{same} task (e.g., from a manual exploration)

\textbf{Case 2:} We have prior observations on \textit{related} tasks (e.g., from HPO on a different dataset)

$\leadsto$ We can inject knowledge to the history of observations or to the surrogate modelling step in Bayesian optimization.

\end{frame}
%-----------------------------------------------------------------------
%----------------------------------------------------------------------
\begin{frame}{Case 1: prior observations from manual exploration}

<copy pseudocode from Bayesian optimization slide deck and highlight that we prepend them to the history>

How does this help? It improves model accuracy. Open question: Do we still need an initial design afterwards?

\end{frame}
%-----------------------------------------------------------------------
%----------------------------------------------------------------------
\begin{frame}{Case 2: prior observations on related tasks}

Assumption: Objectice functions of tasks can correlate. If they do, we can transfer knowledge to speed up search. \\
Aim: Control transfer: Positive transfer from similar tasks, zero transfer from different tasks.

Questions:
\begin{enumerate}
    \item How do we compare tasks and measure similarity?
    \item How do we extract knowledge?
    \item How do we inject it in the new task?
\end{enumerate}

\end{frame}
%-----------------------------------------------------------------------
%----------------------------------------------------------------------
\begin{frame}{Portfolios to warmstart Bayesian Optimization}

Needed: Many heterogeneous tasks.

Add something about greedy portfolio selection. mention that this is great if you have diverse tasks.

\end{frame}
%-----------------------------------------------------------------------
%----------------------------------------------------------------------
\begin{frame}{Meta-features to explicitly measure dataset distance}

Copy content from last edition 

\end{frame}
%-----------------------------------------------------------------------
%----------------------------------------------------------------------
\begin{frame}{Meta-feature-free Transfer learning}

So far, we 

discuss that meta-features are not necessarily good. Discuss other ways, i.e. RGPE or model ensembles

\end{frame}
%-----------------------------------------------------------------------
%----------------------------------------------------------------------
\begin{frame}{What if prior information is misleading?}

add something here about sensitivit of each method to irrelevant tasks

\end{frame}
%-----------------------------------------------------------------------
%----------------------------------------------------------------------
\begin{frame}{Summary}

TBD

\end{frame}


\end{document}
